Simulation Figures for Genome Biology (simulations)

### 2018-07-09 manuscript_figures/manuscript_figures_sims.Rmd
Change informativeness and pi0 sims plots to match Fig2 style

```{r, fig.width = 8, fig.height = 5}
dplyr::filter(res_nullset, key == "FWER") %>%
    filter(! (Method == "ashq" & dist == "chisq4"),
           ! (grepl("scott", Method) & dist == "chisq4")) %>%
    ggplot(aes(x = Method, y = mean_value, color = Method)) +
    geom_point() +
    scale_color_manual(values = col, guide = FALSE) +
    facet_grid(. ~ dist) +
    scale_y_continuous("FWER", breaks = seq(0, 1, .2), labels = scales::percent) +
    theme(axis.text.x = element_text(angle = 90, vjust = 1/2, hjust = 1)) +
    ggtitle("Proportion of replications with at least one false positive (over 100 replications)") 
```

@@

```{r, fig.width = 8, fig.height = 5}
gp <- dplyr::filter(res_nullset, key == "TNR") %>%
    filter(! (Method == "ashq" & dist == "chisq4"),
           ! (grepl("scott", Method) & dist == "chisq4")) %>%
    ggplot(aes(x = Method, y = mean_value, color = Method)) +
    geom_point() +
    geom_errorbar(aes(ymin = mean_value - se, ymax = mean_value + se)) + 
    facet_grid(. ~ dist) +
    scale_y_continuous("TPR", labels = scales::percent) +
    scale_color_manual(values = col, guide = FALSE) +
    theme(axis.text.x = element_text(angle = 90, vjust = 1/2, hjust = 1)) +
    ggtitle("Average TNR (over 100 replications)") 
gp

ggsave(file.path(outdir, "FigureSsim-null.pdf"), gp, width = 8, height = 5)
```

@@

@@

## including SE to show variability in FDRR
pfdr <- dplyr::select(res_pi0set, Method, setting, pi0, key, mean_value, se, col, lty) %>%
    dplyr::filter(key == "FDR", !is.na(mean_value)) %>%
    ggplot(aes(x = pi0 / 100, y = mean_value, color = Method, lty = Method)) +
    geom_line(alpha = 1/6, position = position_dodge(width = .01)) +
    geom_errorbar(aes(ymin = mean_value - se, ymax = mean_value + se), alpha = 1) +
    geom_point(alpha = 1, position = position_dodge(width = .01)) +
    scale_color_manual(values = col) +
    scale_linetype_manual(values = lty) + 
    geom_hline(yintercept = 0.10, color = "red", lty = 2, alpha = 1/3) + 
    scale_x_continuous("Null Proportion", labels = scales::percent, breaks = seq(0, 1, .1)) + 
    scale_y_continuous("FDR", labels = scales::percent) + 
    facet_grid(setting ~ .) + 
    ggtitle("Average FDR Across Varying Null Proportion")

## including SE to show variability in FDRR
ptpr <- dplyr::select(res_pi0set, Method, setting, pi0, key, mean_value, se, col, lty) %>%
    dplyr::filter(key == "TPR", !is.na(mean_value)) %>%
    ggplot(aes(x = pi0 / 100, y = mean_value, color = Method, lty = Method)) +
    geom_line(alpha = 1/6, position = position_dodge(width = .01)) +
    geom_errorbar(aes(ymin = mean_value - se, ymax = mean_value + se), alpha = 1) +
    geom_point(alpha = 1, position = position_dodge(width = .01)) +
    scale_color_manual(values = col) +
    scale_linetype_manual(values = lty) + 
    scale_x_continuous("Null Proportion", labels = scales::percent, breaks = seq(0, 1, .1)) + 
    scale_y_continuous("TPR", labels = scales::percent) + 
    facet_grid(setting ~ .) + 
    ggtitle("Average TPR Across Varying Null Proportion")
```

@@

ggsave(file.path(outdir, "FigureSsim-nullprop.pdf"), gp, width = 15, height = 7.5)

@@

ggsave(file.path(outdir, "FigureSsim-nullprop-zoom.pdf"), gp_zoom, width = 15, height = 7.5)
```

@@

## not including SE because it's too small
pfdr <- dplyr::select(res_infoset, Method, setting, level, key, mean_value, se, q10, q90, col, lty) %>%
    dplyr::filter(key == "FDR") %>%
    ggplot(aes(x = level / 100, y = mean_value, color = Method, lty = Method)) +
    geom_line(alpha = 1/6, position = position_dodge(width = .01)) +
    ##geom_errorbar(aes(ymin = mean_value - se, ymax = mean_value + se), width = 0) +
    geom_point(alpha = 1, position = position_dodge(width = .01)) +
    scale_color_manual(values = col) +
    scale_linetype_manual(values = lty) + 
    geom_hline(yintercept = 0.10, color = "red", lty = 2, alpha = 1/3) + 
    scale_x_continuous("Informativeness", labels = scales::percent, breaks = seq(0, 1, .1)) + 
    scale_y_continuous("FDR", labels = scales::percent) + 
    facet_grid(setting ~ .) + 
    ggtitle("Average FDR Across Varying Informativeness")
pfdr

ptpr <- dplyr::select(res_infoset, Method, setting, level, key, mean_value, se, col, lty) %>%
    dplyr::filter(key == "TPR") %>%
    ggplot(aes(x = level / 100, y = mean_value, color = Method, lty = Method)) +
    geom_line(alpha = 1/6, position = position_dodge(width = .01)) +
    ##geom_errorbar(aes(ymin = mean_value - se, ymax = mean_value + se), width = 0) +    
    geom_point(alpha = 1, position = position_dodge(width = .01)) +
    scale_color_manual(values = col) +
    scale_linetype_manual(values = lty) + 
    scale_x_continuous("Informativeness", labels = scales::percent, breaks = seq(0, 1, .1)) + 
    scale_y_continuous("TPR", labels = scales::percent) + 
    facet_grid(setting ~ ., scales = "free_y") + expand_limits(y = 0) +
    ggtitle("Average TPR Across Varying Informativeness")
ptpr
```

@@

ggsave(file.path(outdir, "FigureSsim-informativeness.pdf"), gp, width = 15, height = 7.5)
```

>>>>

```{r, fig.width = 8, fig.height = 5}
gp_nullA <- dplyr::filter(res_nullset, key == "FWER") %>%
    filter(! (Method == "ashq" & dist == "chisq4"),
           ! (grepl("scott", Method) & dist == "chisq4")) %>%
    ggplot(aes(x = Method, y = mean_value, color = Method)) +
    geom_point() +
    scale_color_manual(values = col, guide = FALSE) +
    facet_grid(. ~ dist) +
    scale_y_continuous("FWER", breaks = seq(0, 1, .2), labels = scales::percent) +
    theme(axis.text.x = element_text(angle = 90, vjust = 1/2, hjust = 1)) +
    ggtitle("Proportion of replications with at least one false positive (over 100 replications)")
gp_nullA
```

@@

```{r, fig.width = 8, fig.height = 5}
gp_nullB <- dplyr::filter(res_nullset, key == "TNR") %>%
    filter(! (Method == "ashq" & dist == "chisq4"),
           ! (grepl("scott", Method) & dist == "chisq4")) %>%
    ggplot(aes(x = Method, y = mean_value, color = Method)) +
    geom_point() +
    geom_errorbar(aes(ymin = mean_value - se, ymax = mean_value + se)) + 
    facet_grid(. ~ dist) +
    scale_y_continuous("TNR", labels = scales::percent) +
    scale_color_manual(values = col, guide = FALSE) +
    theme(axis.text.x = element_text(angle = 90, vjust = 1/2, hjust = 1)) +
    ggtitle("TNR in Null Simulations (over 100 replications)") 
gp_nullB

ggsave(file.path(outdir, "FigureSsim-nullA.pdf"), gp_nullA, width = 8, height = 5)
ggsave(file.path(outdir, "FigureSsim-nullB.pdf"), gp_nullB, width = 8, height = 5)

gp_zoom <- plot_grid(pfdr + coord_cartesian(c(0, .2), c(0, .2)) + guides(color = FALSE, linetype = FALSE),
                     ptpr + coord_cartesian(c(.6, 1), c(.6, 1)), rel_widths = c(1, 1.4), labels = LETTERS[1:2])
ggsave(file.path(outdir, "FigureSsim-null.pdf"), gp, width = 8, height = 5)

```

@@

We notice that under certain settings, the mean and SE FDR values are `NA`s for some methods under some
settings. We take a closer look at these cases.

```{r}
dplyr::select(res_pi0set, setting, Method, pi0, mean_value, key) %>%
    dplyr::filter(key %in% c("rejections", "FDR")) %>%
        tidyr::spread(key, mean_value) %>%
        dplyr::filter(is.na(FDR))
```

All cases correspond to methods and settings where the method rejected 0 tests over all replications.
We deal with these cases by setting these values to zero for plotting purposes.

```{r}
res_pi0set$se[is.na(res_pi0set$mean_value) & res_pi0set$key == "FDR"] <- 0
res_pi0set$mean_value[is.na(res_pi0set$mean_value) & res_pi0set$key == "FDR"] <- 0
```

@@

## including SE to show variability in FDRR
pfdr <- dplyr::select(res_pi0set, Method, setting, pi0, key, mean_value, se, col, lty) %>%
    dplyr::filter(key == "FDR", !is.na(mean_value)) %>%
    ggplot(aes(x = pi0 / 100, y = mean_value, color = Method, lty = Method)) +
    geom_line(alpha = 0.85, position = position_dodge(width = .01)) +
    geom_errorbar(aes(ymin = mean_value - se, ymax = mean_value + se), width=0.025, alpha=0.5) +
    scale_color_manual(values = col) +
    scale_linetype_manual(values = lty) + 
    geom_hline(yintercept = 0.10, color = "red", lty = 2, alpha = 1/3) + 
    scale_x_continuous("Null Proportion", labels = scales::percent, breaks = seq(0, 1, .1)) + 
    scale_y_continuous("FDR", labels = scales::percent) + 
    facet_grid(setting ~ .) + 
    ggtitle("Mean FDR Over 100 Replications") +
    theme_classic() +
    theme(axis.title = element_text(face="bold", size = 10),
          plot.title = element_text(face="bold", size = 14))

## including SE to show variability in FDRR
ptpr <- dplyr::select(res_pi0set, Method, setting, pi0, key, mean_value, se, col, lty) %>%
    dplyr::filter(key == "TPR", !is.na(mean_value)) %>%
    ggplot(aes(x = pi0 / 100, y = mean_value, color = Method, lty = Method)) +
    geom_line(alpha = 0.85, position = position_dodge(width = .01)) +
    geom_errorbar(aes(ymin = mean_value - se, ymax = mean_value + se), width=0.025, alpha=0.5) +
    scale_color_manual(values = col) +
    scale_linetype_manual(values = lty) + 
    scale_x_continuous("Null Proportion", labels = scales::percent, breaks = seq(0, 1, .1)) + 
    scale_y_continuous("TPR", labels = scales::percent) + 
    facet_grid(setting ~ .) + 
    ggtitle("Mean TPR Over 100 Replications") +
    theme_classic() +
    theme(axis.title = element_text(face="bold", size = 10),
          plot.title = element_text(face="bold", size = 14))
```

@@

ggsave(file.path(outdir, "FigureSsim-nullprop.pdf"), gp, width = 10, height = 5)

@@

ggsave(file.path(outdir, "FigureSsim-nullprop-zoom.pdf"), gp_zoom, width = 10, height = 5)
```

@@

## including SE to show variability in FDRR
pfdr <- dplyr::select(res_pi0set, Method, setting, pi0, key, mean_value, se, col, lty) %>%
    dplyr::filter(key == "FDR", !is.na(mean_value)) %>%
    ggplot(aes(x = pi0 / 100, y = mean_value, color = Method, lty = Method)) +
    geom_line(alpha = 0.85, position = position_dodge(width = .01)) +
    geom_errorbar(aes(ymin = mean_value - se, ymax = mean_value + se), width=0.025, alpha=0.5) +
    scale_color_manual(values = col) +
    scale_linetype_manual(values = lty) + 
    geom_hline(yintercept = 0.10, color = "red", lty = 2, alpha = 1/3) + 
    scale_x_continuous("Null Proportion", labels = scales::percent, breaks = seq(0, 1, .1)) + 
    scale_y_continuous("FDR", labels = scales::percent) + 
    facet_grid(setting ~ .) + 
    ggtitle("Mean FDR Over 100 Replications") +
    theme_classic() +
    theme(axis.title = element_text(face="bold", size = 10),
          plot.title = element_text(face="bold", size = 14))

## not including SE because it's too small
pfdr <- dplyr::select(res_infoset, Method, setting, level, key, mean_value, se, q10, q90, col, lty) %>%
    dplyr::filter(key == "FDR") %>%
    ggplot(aes(x = level / 100, y = mean_value, color = Method, lty = Method)) +
    geom_line(alpha = 0.85, position = position_dodge(width = .01)) +
    geom_errorbar(aes(ymin = mean_value - se, ymax = mean_value + se), width=0.025, alpha=0.5) +
    scale_color_manual(values = col) +
    scale_linetype_manual(values = lty) + 
    geom_hline(yintercept = 0.10, color = "red", lty = 2, alpha = 1/3) + 
    scale_x_continuous("Informativeness", labels = scales::percent, breaks = seq(0, 1, .1)) + 
    scale_y_continuous("FDR", labels = scales::percent) + 
    facet_grid(setting ~ .) + 
    ggtitle("Mean FDR Over 100 Replications") +
    theme_classic() +
    theme(axis.title = element_text(face="bold", size = 10),
          plot.title = element_text(face="bold", size = 14))
pfdr

ptpr <- dplyr::select(res_infoset, Method, setting, level, key, mean_value, se, col, lty) %>%
    dplyr::filter(key == "TPR") %>%
    ggplot(aes(x = level / 100, y = mean_value, color = Method, lty = Method)) +
    geom_line(alpha = 0.85, position = position_dodge(width = .01)) +
    geom_errorbar(aes(ymin = mean_value - se, ymax = mean_value + se), width=0.025, alpha=0.5) +
    scale_color_manual(values = col) +
    scale_linetype_manual(values = lty) + 
    scale_x_continuous("Informativeness", labels = scales::percent, breaks = seq(0, 1, .1)) + 
    scale_y_continuous("TPR", labels = scales::percent) + 
    facet_grid(setting ~ ., scales = "free_y") + expand_limits(y = 0) +
    ggtitle("Mean TPR Over 100 Replications") +
    theme_classic() +
    theme(axis.title = element_text(face="bold", size = 10),
          plot.title = element_text(face="bold", size = 14))
ptpr
```

@@

```{r, fig.width = 15, fig.height = 7.5}
gp <- plot_grid(pfdr + guides(color = FALSE, linetype = FALSE), ptpr,
          rel_widths = c(1, 1.25), labels = LETTERS[3:4])
gp

ggsave(file.path(outdir, "FigureSsim-informativeness.pdf"), gp, width = 10, height = 5)
```
